Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-01 public/paper/pyg4ometry.tex
fluka paper bits

The FLUKA CSG ASCII format is parsed using an ANTLR4-generated parser,
producing an abstract syntax tree (AST).  The resulting AST is then
walked to populate Region instances with zones and bodies.  An example
FLUKA region with the corresponding abstract syntax tree is shown in
Figure~\ref{fig:region-ast}.
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=1.0\textwidth]{./model-scene/faradayCup2.pdf}
\caption{Example conversion of a simple FLUKA geometry to GDML, left panel :  
the original FLUKA geometry displayed in FLAIR, right panel : the GDML geometry 
viewed in pyg4ometry. The example is a Faraday cup used to capture 
and measure accelerator beam charge.}
\label{fig:region-ast}
\end{center}
\end{figure*}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=6cm]{./diagrams/lattice}
\caption{The \fluka{lattice} feature demonstrating a \fluka{lattice} cell
  referring to its basic unit with the rototranslation $R_\textrm{trans}$.
  Any particle entering the cell will be transformed onto the basic unit
  with $R\textrm{trans}$, and when leaving the basic unit, back to the cell
  with $R_\textrm{trans}^{-1}$.}
\label{fig:lattice}
\end{center}
\end{figure}

>>>>

The FLUKA CSG ASCII format is parsed using an ANTLR4-generated parser,
producing an abstract syntax tree (AST).  The resulting AST is then walked
to populate Region instances with zones and bodies.  With the region
instances populated they can then be manipulated and translated into GDML.
The translation involves a number of special steps to bridge the two
disparate formats and ensure the resulting GDML is well-formed ans usable
in Geant4.  Some of these steps are simple, for example in FLUKA unions can
be disconnected, but in Geant4 specifically only MultiUnions can be
disconnected, such that MultiUnions are used throughout the converted
geometry instead of the usual binary unions.  Other procedures are more
involved and are discussed in the rest of this section.

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=1.0\textwidth]{./model-scene/faradayCup2.pdf}
\caption{Example conversion of a simple FLUKA geometry to GDML, left panel :  
the original FLUKA geometry displayed in FLAIR, right panel : the GDML geometry 
viewed in pyg4ometry. The example is a Faraday cup used to capture 
and measure accelerator beam charge.}
\label{fig:region-ast}
\end{center}
\end{figure*}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=6cm]{./diagrams/lattice}
\caption{The \fluka{lattice} feature demonstrating a \fluka{lattice} cell
  referring to its basic unit with the rototranslation $R_\textrm{trans}$.
  Any particle entering the cell will be transformed onto the basic unit
  with $R_\textrm{trans}$, and when leaving the basic unit, back to the cell
  with $R_\textrm{trans}^{-1}$.}
\label{fig:lattice}
\end{center}
\end{figure}
